Model Finding for Recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples utilisables par Isabelle et Coq'' (CUIC). }

### 2015-06-01 tex/camera_ready/paper.tex
added camera-ready and make fit on 11 pages

@@

The Leon system~\cite{blanc2013overview} implements a procedure that can
produce both proofs and counter\-examples for properties of terminating functions
written in a subset of Scala. Leon is based on an SMT solver. It avoids
quantifiers altogether by unfolding recursive definitions up to a certain
depth, which is increased on a per-need basis.
Our translation~$\conv$ works in an analogous manner, 
where instead the SMT solver is invoked only once 
and where quantifier instantiation amounts to function unfolding.
\begin{longv}It would be
worth investigating how existing approaches for function
unfolding can inform approaches for dedicated quantifier instantiation
techniques for function definitions, and vice versa.\end{longv}

@@

%\begin{nottinyv}
{%\footnotesize
\def\ackname{Acknowledgment}
\paragraph{%\footnotesize
\ackname.}
Viktor Kuncak and Stephan Merz have made this work possible. We would also like
to thank Damien Busato-Gaston and Emmanouil Koukoutos for providing the initial
set of benchmarks used in the evaluation.
}
%\end{nottinyv}

{
\bibliographystyle{abbrv}
\bibliography{bib}
}

>>>>

\PassOptionsToClass{11pt,withtimes}{easychair}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{scaled=.86}{helvet}
\PassOptionsToPackage{
   a4paper,
   pdftex,
   pdftitle={Model Finding for Recursive Functions in SMT},
   pdfauthor={Andrew Reynolds, Jasmin Christian Blanchette, and Cesare Tinelli},
   pdfkeywords={},
   pdfborder={0 0 0},
   draft=false,
   bookmarksnumbered,
   bookmarks,
   bookmarksdepth=2,
   bookmarksopenlevel=2,
   bookmarksopen}{hyperref}
\documentclass{easychair}

%envcountsect,
\usepackage{version}

\excludeversion{tinyv}
\includeversion{nottinyv}
\includeversion{shortv}
\excludeversion{longv}

@@

The Leon system~\cite{blanc2013overview} implements a procedure that can
produce both proofs and counter\-examples for properties of terminating functions
written in a subset of Scala. Leon is based on an SMT solver. It avoids
quantifiers altogether by unfolding recursive definitions up to a certain
depth. %, which is increased on a per-need basis.
Our translation~$\conv$ works in an analogous manner, 
where instead the SMT solver is invoked only once 
and where quantifier instantiation amounts to function unfolding.
\begin{longv}It would be
worth investigating how existing approaches for function
unfolding can inform approaches for dedicated quantifier instantiation
techniques for function definitions, and vice versa.\end{longv}

@@

%\begin{nottinyv}
{%\footnotesize
\def\ackname{Acknowledgment}
\paragraph{%\footnotesize
\ackname.}
Viktor Kuncak and Stephan Merz have made this work possible. We would also like
to thank Damien Busato-Gaston and Emmanouil Koukoutos for providing the initial
set of benchmarks used in the evaluation, and the anonymous reviewers for their
suggestions and comments.
}
%\end{nottinyv}

{
\bibliographystyle{abbrv}
%\bibliography{bib}

\begin{thebibliography}{10}

\bibitem{barrett-et-al-2011}
C.~Barrett, C.~L. Conway, M.~Deters, L.~Hadarean, D.~Jovanovic, T.~King,
  A.~Reynolds, and C.~Tinelli.
\newblock {CVC4}.
\newblock In G.~Gopalakrishnan and S.~Qadeer, editors, {\em CAV 2011}, volume
  6806 of {\em LNCS}, pages 171--177. Springer, 2011.

\bibitem{smtlib25}
C.~Barrett, P.~Fontaine, and C.~Tinelli.
\newblock The {SMT-LIB} standard---{V}ersion 2.5.
\newblock \url{http://smt-lib.org/language.shtml}, to appear.

\bibitem{baumgartner-et-al-2009}
P.~Baumgartner, A.~Fuchs, H.~de~Nivelle, and C.~Tinelli.
\newblock Computing finite models by reduction to function-free clause logic.
\newblock {\em J. Applied Logic}, 7(1):58--74, 2009.

\bibitem{blanc2013overview}
R.~Blanc, V.~Kuncak, E.~Kneuss, and P.~Suter.
\newblock An overview of the {Leon} verification system---{V}erification by
  translation to recursive functions.
\newblock In {\em Scala {'}13}. ACM, 2013.

\bibitem{blanchette-nipkow-2010}
J.~C. Blanchette and T.~Nipkow.
\newblock Nitpick: A counterexample generator for higher-order logic based on a
  relational model finder.
\newblock In M.~Kaufmann and L.~C. Paulson, editors, {\em ITP 2010}, volume
  6172 of {\em LNCS}, pages 131--146. Springer, 2010.

\bibitem{claessen-hughes-2000}
K.~Claessen and J.~Hughes.
\newblock Quick{C}heck: A lightweight tool for random testing of {H}askell
  programs.
\newblock In {\em ICFP {'}00}, pages 268--279. ACM, 2000.

\bibitem{claessen-sorensson-2003}
K.~Claessen and N.~S{\"o}rensson.
\newblock New techniques that improve {MACE}-style model finding.
\newblock In {\em MODEL}, 2003.

\bibitem{MouraBjoerner07}
L.~de~Moura and N.~Bj{\o}rner.
\newblock Efficient {E}-matching for {SMT} solvers.
\newblock In F.~Pfenning, editor, {\em CADE-21}, volume 4603 of {\em LNCS},
  pages 183--198. Springer, 2007.

\bibitem{de-moura-bjoerner-2008}
L.~de~Moura and N.~Bj{\o}rner.
\newblock {Z3}: {An} efficient {SMT} solver.
\newblock In C.~R. Ramakrishnan and J.~Rehof, editors, {\em TACAS 2008}, volume
  4963 of {\em LNCS}, pages 337--340. Springer, 2008.

\bibitem{dunets-et-al-2010}
A.~Dunets, G.~Schellhorn, and W.~Reif.
\newblock Automated flaw detection in algebraic specifications.
\newblock {\em J.~Autom.\ Reasoning}, 45(4):359--395, 2010.

\bibitem{GeDeM-CAV-09}
Y.~Ge and L.~de~Moura.
\newblock Complete instantiation for quantified formulas in satisfiability
  modulo theories.
\newblock In {\em CAV '09}, volume 5643 of {\em LNCS}, pages 306--320.
  Springer, 2009.

\bibitem{DBLP:conf/itp/JohanssonDB10}
M.~Johansson, L.~Dixon, and A.~Bundy.
\newblock Case-analysis for rippling and inductive proof.
\newblock In {\em {ITP} 2010}, pages 291--306, 2010.

\bibitem{korovin-2013}
K.~Korovin.
\newblock Non-cyclic sorts for first-order satisfiability.
\newblock In P.~Fontaine, C.~Ringeissen, and R.~A. Schmidt, editors, {\em
  FroCoS 2013}, volume 8152 of {\em LNCS}, pages 214--228. Springer, 2013.

\bibitem{krauss-2009-phd}
A.~Krauss.
\newblock {\em Automating Recursive Definitions and Termination Proofs in
  Higher-Order Logic}.
\newblock {Ph.D.}\ thesis, Technische Universit\"at M\"unchen, 2009.

\bibitem{kuncak-jackson-2005}
V.~Kuncak and D.~Jackson.
\newblock Relational analysis of algebraic datatypes.
\newblock In M.~Wermelinger and H.~Gall, editors, {\em ESEC/FSE 2005}. ACM,
  2005.

\bibitem{mccune-1994}
W.~McCune.
\newblock A {D}avis--{P}utnam program and its application to finite first-order
  model search: Quasigroup existence problems.
\newblock Technical report, Argonne National Laboratory, 1994.

\bibitem{reynolds-blanchette-2015-codata}
A.~Reynolds and J.~C. Blanchette.
\newblock A decision procedure for (co)datatypes in {SMT} solvers.
\newblock In A.~Felty and A.~Middeldorp, editors, {\em CADE-25}, LNCS.
  Springer, 2015.

\bibitem{our-report}
A.~Reynolds, J.~C. Blanchette, and C.~Tinelli.
\newblock Model finding for recursive functions in {SMT}.
\newblock Tech.\ report, \url{http://lara.epfl.ch/~reynolds/SMT2015-recfun/},
  2015.

\bibitem{reynolds-kuncak-2015}
A.~Reynolds and V.~Kuncak.
\newblock Induction for {SMT} solvers.
\newblock In D.~D'Souza, A.~Lal, and K.~G. Larsen, editors, {\em {VMCAI} 2015},
  volume 8931 of {\em LNCS}, pages 80--98. Springer, 2014.

\bibitem{ReynoldsTinelliMoura14}
A.~Reynolds, C.~Tinelli, and L.~de~Moura.
\newblock Finding conflicting instances of quantified formulas in {SMT}.
\newblock In {\em FMCAD 2014}, pages 195--202. {IEEE}, 2014.

\bibitem{ReyEtAl-1-RR-13}
A.~Reynolds, C.~Tinelli, A.~Goel, and S.~Krsti\'c.
\newblock Finite model finding in {SMT}.
\newblock In N.~Sharygina and H.~Veith, editors, {\em CAV 2013}, volume 8044 of
  {\em LNCS}, pages 640--655. Springer, 2013.

\bibitem{reynolds-et-al-2013}
A.~Reynolds, C.~Tinelli, A.~Goel, S.~Krsti{\'c}, M.~Deters, and C.~Barrett.
\newblock Quantifier instantiation techniques for finite model finding in
  {SMT}.
\newblock In M.~P. Bonacina, editor, {\em CADE-24}, volume 7898 of {\em LNCS},
  pages 377--391. Springer, 2013.

\bibitem{slaney-1994}
J.~K. Slaney.
\newblock {FINDER}: Finite domain enumerator system description.
\newblock In A.~Bundy, editor, {\em CADE-12}, volume 814 of {\em LNCS}, pages
  798--801. Springer, 1994.

\bibitem{torlak-jackson-2007}
E.~Torlak and D.~Jackson.
\newblock Kodkod: A relational model finder.
\newblock In O.~Grumberg and M.~Huth, editors, {\em TACAS 2007}, volume 4424 of
  {\em {LNCS}}, pages 632--647. Springer, 2007.

\bibitem{weber-2008}
T.~Weber.
\newblock {\em SAT-Based Finite Model Generation for Higher-Order Logic}.
\newblock {Ph.D.}\ thesis, Technische Universit\"at M\"unchen, 2008.

\bibitem{zhang-zhang-1995}
J.~Zhang and H.~Zhang.
\newblock {SEM}: A system for enumerating models.
\newblock In C.~S. Mellish, editor, {\em IJCAI-95}, volume~1, pages 298--303.
  Morgan Kaufmann, 1995.

\end{thebibliography}
}
